Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-15 latex/article.tex

\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and  Jonathan
  Dupuy\inst{1}\inst{2}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{3} }

@@

 \institute{ Universit\'e de Lyon, CNRS\\
   INSA-Lyon, LIRIS, UMR5205, F-69621, France
%   \email{\{david.coeurjolly,jeremy.levallois\}@liris.cnrs.fr}
   \and
 Universit\'ee de Montr\'eeal\\
LIGUM, Dept. I.R.O., Canada\\
\and
Universit\'e de Savoie, CNRS\\
LAMA, UMR5127, F-73776, France\\
%\email{jacques-olivier.lachaud@univ-savoie.fr}
}

@@

\keywords{isosurface visualization, Digital Geometry, Curvature estimation}
\end{abstract}

>>>>

\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }

@@

 \institute{ Universit\'e de Lyon, CNRS\\
   LIRIS, UMR5205, F-69621, France
%   \email{\{david.coeurjolly,jeremy.levallois\}@liris.cnrs.fr}
   \and
Universit\'e de Savoie, CNRS\\
LAMA, UMR5127, F-73776, France\\
%\email{jacques-olivier.lachaud@univ-savoie.fr}
}

@@

\keywords{Isosurface Visualization, Digital Geometry, Curvature
  Estimation, GPU.}
\end{abstract}
